How to compute the fusion product of MV cycles in type A

### 2021-04-14 draft.tex
Updates from Overleaf

\begin{example}
Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
\[
\young(2,4) \text{ and } \young(13,2,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(112,24,3) \text{ and } \young(13,2,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
     & & & 0 & 1 & & & & & \\
     & & & & 0 & 1 & & & & \\
     & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
     & & & & & & 0 & 1 & & \\
     & & & & & & & s & A_{34}^1 & A_{34}^2 \\
     & & & & & & & & 0 & 1 \\
     & & & & & & & & & s
\end{BMAT}
\right]
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
    X_3 & A_{13}^1,A_{23}^1 \\
    X_4 & \begin{array}{c}
         A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
         A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
         A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
    \end{array} 
\end{array}.
\]
Our ideal decomposes into 
\[
\langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
\cap \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle.
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
\end{array}
\]
so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
\end{example}

>>>>

\begin{example}
Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
\[
\young(2,4) \text{ and } \young(13,2,4).
\]
As the sum of the weights is not dominant, we will instead be using the tableaux
\[
\young(112,24,3) \text{ and } \young(13,2,4).
\]
Our matrix is 
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
     & & & 0 & 1 & & & & & \\
     & & & & 0 & 1 & & & & \\
     & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
     & & & & & & 0 & 1 & & \\
     & & & & & & & s & A_{34}^1 & A_{34}^2 \\
     & & & & & & & & 0 & 1 \\
     & & & & & & & & & s
\end{BMAT}
\right]
\]
The relations from the submatrices are:
\[
\begin{array}{c|c}
    \text{Submatrix} & \text{Relations} \\ \hline
    X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
    X_3 & A_{13}^1,A_{23}^1 \\
    X_4 & \begin{array}{c}
         A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
         A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
         A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
         A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
    \end{array} 
\end{array}.
\]
Hence our ideal decomposes into 
\[
\langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
\cap \begin{array}{c}
     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
\end{array} 
\]
The tableau for each ideal is
\[\begin{array}{cccc}\vspace{1mm}
    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
    \begin{array}{c}
     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
\end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
\end{array}
\]
so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
\end{example}
